---
title: "OED modeling pipeline"
output: html_notebook
---

This documents a start-to-finish pipeline for generating OED designs of MAC/GMC tensile tests. In the interest of brevity, there is no mathematical or mechanical theory here. 

```{r}
library(MaterialAnalysis)
```

# Step 1 – Generate mac files

The MAC files are generated in sections (constituents, laminates, mechanical loading, failure conditions, the solver, the print level, and the plotting options [if any]). 

## Constituents

```{r}
## From example 1 in Manual 
const <- data.frame(M=1:2, CMOD=6, MATID="U", MATDB=1)
mat_props <- data.frame(
  E_A=c(388.2, 3.45), E_T=c(7.6,3.45), V_A=c(0.41,0.35), V_T=c(14.9,1.278), G_A=c(14.9,1.278),
  alpha_A=c(-0.68,45), alpha_T=c(9.74,45)
)
const_full <- cbind(const, mat_props, name=c("Graphite Fiber", "Epoxy Matrix"))
```


## Configure Layups
```{r}
## Layups to test 
layups <- c("[0]_24", 
            "[90]_24", 
            "[0/90]_12", 
            "[0/90]_6S", 
            "[15, -15]_12", 
            "[30, -30]_12",
            "[45, -45]_12",
            "[60, -60]_12", 
            "[75, -75]_12",
            "[15, -15]_6S",
            "[30, -30]_6S",
            "[45, -45]_6S",
            "[60, -60]_6S",
            "[75, -75]_6S",
            "[0, -45, 45, 90]_3S", 
            "[0, -60, 60]_4S", 
            "[0, 90, -30, 30, -60, 60]_2S", 
            "[0, 45, 90, -45]_6", 
            "[45, -45, 90, 0]_3S") 

## Matrix of laminate layups; each column is a layup 
lam_layups <- sapply(layups, makeLayup)
```

Generate the MAC files. 



These are strings parameterized 
```{r}

## Remove previous files
sapply(list.files("~/GENERATED_MAC/"), function(fn) file.remove(file.path("~/GENERATED_MAC", fn)))

# Simulating graphite and epoxy laminates
cc <- 1L
for (i in 1:500){

  ## Graphite fiber 
  mat1 <- list(M=1, CMOD=6, MATID="U", MATDB=1)
  
  E_A <- rnorm(n = 1, mean = 388200, sd = 388200*0.03)
  fiber_str <- rnorm(n = 1, mean = 3500, sd = 3500*0.05)
  
  E_Am <- rnorm(n = 1, mean = 3450, sd = 3450*0.03)
  matrix_str <- rnorm(n = 1, mean = 80, sd = 80*0.05)
  
  G_A <- rnorm(n = 1, mean = 14900, sd= 14900*0.03)
  V <- E_A/2*G_A -1 
  mat1 <- append(mat1, list(EL=c(E_A,E_A,V,V,G_A,-0.68,9.74))) # moduli in MPa
  
  E_Am <- rnorm(n = 1, mean = 3450, sd = 3450*0.03)
  G_Am <- rnorm(n = 1, mean = 1280, sd = 1280*0.03)
  Vm <- E_Am/2*G_Am -1 
  mat2 <- list(M=2, CMOD=6, MATID="U", MATDB=1)
  mat2 <- append(mat2, list(EL=c(E_Am,E_Am,Vm,Vm,G_Am,45,45))) # moduli in MPa
  
  ## Form the constituents section
  constituents <- list("*CONSTITUENTS", "  NMATS=2", paste0("  ", parse_row(mat1)), paste0("  ", parse_row(mat2)))
  
  for (li in 1:length(layups)){
    clam <- eval(as.symbol(paste0("lam", li)))
    
    ## Form simple laminate
    n_ply <- 24
    lam_vf <- rnorm(n_ply, mean = 0.60, sd = 0.60*0.03)
    cangles <- rnorm(length(clam), mean = clam, sd = abs(clam*0.01))
    lam_def <- data.frame(LY=1:n_ply, MOD=2, THK=1/n_ply, ANG=cangles, ARCHID=1, VF=lam_vf, "F"=1, M=2)
    laminate <- append(list("*LAMINATE", sprintf("  NLY=%d", n_ply)), as.list(paste0("   ", parse_df(lam_def))))
    
    ## Apply a fixed mechanical load
    mech <- data.frame(NPT=rep(2L, 6), TI=rep("0.,1.", 6L), MAG=c("0.,0.05", rep("0.,0.", 5L)), 
                       MODE=c(1, rep(2, 5)))
    mload <- append(list("*MECH", "  LOP=99"), as.list(parse_df(mech, pre_space = "  ")))
    
    ## Static failure analysis 
    criteria <- "   CRIT=%d X11=%f COMPR=SAM ACTION=1"
    sfa <- list("*FAILURE_SUBCELL", " NMAT=2", 
                "  MAT=1 NCRIT=1", sprintf(criteria, 1, fiber_str), 
                "  MAT=2 NCRIT=1", sprintf(criteria, 1, matrix_str))
    
    ## Solver 
    solver_settings <- list(METHOD=1, NPT=2, TI="0., 1.", STP=0.001, ITMAX=20, ERR=1e-4)
    solver <- list("*SOLVER", paste0("  ", parse_row(solver_settings)))
    
    ## Output section
    out <- list("*PRINT", "  NPL=3")
    
    ## Get the stress strain output as well 
    ss_out <- list("*XYPLOT", "  FREQ=1", "  LAMINATE=1", 
                   sprintf("  NAME=graphite_epoxy_ss%d X=1 Y=10", cc), 
                   "  MACRO=0", "  MICRO=0")
    
    ## Generate test mac files
    mac_file <- c(constituents, laminate, mload, sfa, solver, out, ss_out, "*END")
    readr::write_lines(mac_file, path = sprintf("~/GENERATED_MAC/graphite_epoxy_%d.mac", cc))
    cc <- cc + 1L
  }
}

```

Run MAC/GMC 

```{r}
library("MaterialAnalysis")
Sys.setenv("pass"="...")
runMAC(src_dir = "~/test_gen_mac", dest_dir = "/acp/u/jstuckne/testing", base_fn = "graphite_epoxy",
       user = "jstuckne", pass = Sys.getenv("pass"))
```


# Step 2 – Run mac

```{r}
MaterialAnalysis::runMAC()
```


# Step 3 – Parse mac output

# Step 4 – train neural network

# Step 5 – perform OED


