---
title: "PMC Experiment"
author: "Joshua Stuckner"
date: "11/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Experiment goal
1. Train a neural network to mimic Mac/GMC with varying volume fraction.
2. Use OED to determine the optimal volume fraction and layup to infer the unknown constituent properties

## Include Libraries
```{r echo=FALSE}
library(MaterialAnalysis)
library(reticulate)
use_python("C:/Users/jstuckne/AppData/Local/Continuum/miniconda3/envs/r-reticulate/python.exe", required=TRUE)
library(keras)
source('~/Code/MaterialAnalysis/MaterialAnalysis/R/NN.R')
library(ggplot2)
library("rmi")
library(tidyverse)
library("lhs")
```

## Get training data from Mac/GMC
# Select layups
```{r}
#Layups to test 
layups <- c("[0]_24", 
            "[90]_24", 
            "[0/90]_6S", 
            "[15, -15]_6S",
            "[30, -30]_6S",
            "[45, -45]_6S",
            "[60, -60]_6S",
            "[75, -75]_6S",
            "[0, -45, 45, 90]_3S", 
            "[0, -60, 60]_4S", 
            "[0, 90, -30, 30, -60, 60]_2S", 
            "[0, 45, 90, -45]_3S", 
            "[45, -45, 90, 0]_3S") 

## Matrix of laminate layups; each column is a layup 
lam_layups <- sapply(layups, MaterialAnalysis::makeLayup)
```

#Create MAC input files
```{r eval=FALSE}
generateMAC(folder = "~/CurrentProjects/Matt_MacGMC/PMC_Class/MAC_DATA_Test_speed/",
            number_to_generate_per_laminate_type = 100,
            delete_old = TRUE,
            uniform_variation = TRUE,
            n_ply = 24,
            E_fiber_nominal = 80000,
            E_fiber_percent_variation = 25,
            UTS_fiber_nominal = 3800,
            UTS_fiber_percent_variation = 25,
            nu_fiber_nominal = 0.25,
            nu_fiber_percent_variation = 20,
            E_matrix_nominal = 4000,
            E_matrix_percent_variation = 25,
            UTS_matrix_nominal = 80,
            UTS_matrix_percent_variation = 40,
            nu_matrix_nominal = 0.35,
            nu_matrix_percent_variation = 10,
            volume_fraction_nominal = .55,
            volume_fraction_variation = 0.15,
            angle_degree_variation = 0,
            max_strain = 0.1)
```

# Run MAC/GMC on the cluster
```{r eval=FALSE}
runMAC(src_dir = "~/CurrentProjects/Matt_MacGMC/PMC_Class/MAC_DATA_Test_speed/", dest_dir = "/acp/u/jstuckne/testing", base_fn = "graphite_epoxy",user = "jstuckne", n_jobs=80)

# pscp jstuckne@cryoterm1:/acp/u/jstuckne/testing2/*.data "C:/Users/jstuckne/OneDrive - NASA/Documents/CurrentProjects/Matt_MacGMC/PMC_Class/MAC_DATA/"
```

# Parse the output files
```{r eval=FALSE}
## Location of mac output files
mac_folder <- "~/CurrentProjects/Matt_MacGMC/PMC_Class/MAC_DATA/"

## Get a list of mac files
res_files <- list.files(mac_folder)

## Get MAC input properties
res_mac <- pbapply::pblapply(res_files[grep(res_files, pattern = "*.mac")], function(mac_file){
  parseMAC(file_path = normalizePath(file.path(mac_folder, mac_file)))
})

## Get the resulting outputs from GMC
res_out <- pbapply::pblapply(res_files[grep(res_files, pattern = "*.out")], function(out_file){
  parseOUT(file_path = normalizePath(file.path(mac_folder, out_file)))
})

## Get the stress strain curves
parseDATA <- function(file_path){
  read.delim(file_path, header=FALSE, sep = "")
}
res_data <- pbapply::pblapply(res_files[grep(res_files, pattern = "*.data")], function(data_file){
  parseDATA(file_path = normalizePath(file.path(mac_folder, data_file)))
})


## Get the inferred stress-stress properties
res_ss <- pbapply::pblapply(res_data[1:10], function(ss){
  getStressStrainStats(strain = tail(ss[, 1],-3), stress = tail(ss[, 2],-3))
})
res_ss_props <- data.table::rbindlist(lapply(res_ss, as.list))

# Save the parsed data
experiment <- list(res_mac, res_out, res_data, res_ss_props)
save(experiment, file = "~/CurrentProjects/Matt_MacGMC/PMC_Class/parsed.rdata")
```

# Load the data
```{r}
## load the inputs 
load("~/CurrentProjects/Matt_MacGMC/PMC_Class/parsed.rdata")
res_mac <- experiment[[1]] 
res_out <- experiment[[2]]
res_data <- experiment[[3]]
res_ss_props <- experiment[[4]]
```

Plot the results
```{r}

{
idx = 14
num = length(layups)
start = (idx-1)*num+1
ii <- start - 1
sapply(res_data[start:(start+num-1)], FUN = function(data){
  ii <<- ii + 1
  ind = ii %% num
  if (ind == 0) {ind = num}
  tit = layups[ind]
  plot(data$V1, data$V2, col=alpha('black', 1), xlab='strain', ylab='stress', main=tit)
  abline(0,res_ss_props[ii,5], col='red', lwd=2)
  points(res_ss_props[ii,4], res_ss_props[ii,3], pch=4, col='red', lwd=3, cex=2)
  points(res_ss_props[ii,2], res_ss_props[ii,1], pch=1, col='red', lwd=3, cex=2)
  #abline(0,ss_predicted[ii,5], col='green', lwd=2)
  #points(ss_predicted[ii,4], ss_predicted[ii,3], pch=4, col='green', lwd=3, cex=2)
  #points(ss_predicted[ii,2], ss_predicted[ii,1], pch=1, col='green', lwd=3, cex=2)
})

}
```

## Train the NN
```{r eval=FALSE}
## Normalize closure
normalizer <- function(x, a = -1, b = 1, rng=NULL){ 
  # if (!is.null(opts) list("ab_range"=list(a=0, b=1), =list(center=TRUE, scale=TRUE))
  if (is.vector(x)){
    { min_x <- min(x); max_x <- max(x) }
    normalize <- function(x, invert=FALSE){ 
      if (missing(invert) || !invert){ return(((b - a)*(x - min_x)) / (max_x - min_x) + a ) }
      else { return(((x - a)/(b - a))*(max_x - min_x) + min_x) }
    }
    return(normalize)
  }
  else if (is.matrix(x)){
    d_x <- ncol(x)
    if (missing(rng) || is.null(rng)){ 
      col_idx <- as.list(seq(ncol(x)))
      x_rng <- apply(x, 2, range)
    } else { 
      if (sum(rng) != d_x) { stop("'rng' should sum to the number fo columns in x.")}
      start_idx <- cumsum(rng) - rng + 1
      col_idx <- lapply(1:length(rng), function(i) start_idx[i]:(start_idx[i]+rng[i]-1L))
      x_rng <- sapply(1:length(col_idx), function(i) { range(as.vector(unlist(x[, col_idx[[i]]]))) })  
    }
    normalize <- function(x, invert=FALSE){ 
      if (missing(invert) || !invert){ 
        x_norm <- matrix(0, ncol = ncol(x), nrow = nrow(x))
        for (i in 1:length(col_idx)){
          idx <- col_idx[[i]]
          x_tmp <- as.vector(unlist(x[, idx]))
          x_norm[, idx] <- ((b - a)*(x_tmp - x_rng[1, i])) / (x_rng[2, i] - x_rng[1, i]) + a 
        }
        return(x_norm) 
      }
      else {
        x_unnorm <- matrix(0, ncol = ncol(x), nrow = nrow(x))
        for (i in 1:length(col_idx)){
          idx <- col_idx[[i]]
          x_tmp <- as.vector(unlist(x[, idx]))
          x_unnorm[, idx] <- (((x_tmp - a)/(b - a))*(x_rng[2, i] - x_rng[1, i]) + x_rng[1, i]) 
        }
        return(x_unnorm)
      }
    }
  }
  return(normalize)
}

## Inputs (constituent properties, fiber volume fractions [per ply], layup, and ABD components)

fiber_props <-  do.call(rbind, lapply(res_mac, function(mac) mac$fiber_constituent_properties[c(1, 3, 8)]))
matrix_props <-  do.call(rbind, lapply(res_mac, function(mac) mac$matrix_constituent_properties[c(1, 3, 8)]))
fiber_vf <- do.call(rbind, lapply(res_mac, function(mac) mac$laminate_properties$VF[1]))
lam_props <- do.call(rbind, lapply(res_out, function(rout) c(rout$Exx, rout$Nxy)))

## Separate out the laminates by the layup 
layup_class <- sapply(res_mac, function(mac){
  which.min(apply(lam_layups, 2, function(lu) sum((lu - mac$laminate_properties$ANG)^2))) 
})
layup_one_hot <- to_categorical(y = layup_class - 1L, num_classes = length(layups))

# without ABD, orientations, and only 1 VF
X_tmp = cbind(fiber_props, matrix_props, fiber_vf)
X_normalizer <- normalizer(X_tmp,
                           rng = c(rep(1, ncol(fiber_props) + ncol(matrix_props)),
                                   ncol(fiber_vf)))
X <- cbind(layup_one_hot, X_normalizer(X_tmp)) ## ensure any(is.na(X)) == FALSE

## Outputs (properties along the stress strain curve)
# c_ss_props <- as.matrix(res_ss_props[c_layup_idx,])
c_ss_props <- cbind(as.matrix(res_ss_props), lam_props[,2]) # USE Nxy
c_ss_props <- cbind(as.matrix(res_ss_props)) # DON'T USE Nxy
Y_normalizer <- normalizer(c_ss_props)
Y <- Y_normalizer(c_ss_props)

## Configure the inputs 
X <- data.table::data.table(X)
data_splits <- partition(X = X, Y = Y, input_shape = c(ncol(X)), 
                         splits = c(train = 0.70, validate = 0.20, test = 0.10))

## The model layers
decision_layers <- list(
  "dense" = list(units = 120, activation = 'relu'),
  "dropout" = list(rate = 0.35),
  "dense" = list(units = 80, activation = 'relu'),
  "dropout" = list(rate = 0.35),
  "dense" = list(units = 80, activation = 'relu'),
  "dropout" = list(rate = 0.35),
  "dense" = list(units = 80, activation = 'relu'),
  "dropout" = list(rate = 0.35),
  "dense" = list(units = 60, activation = 'relu'),
  "dropout" = list(rate = 0.35),
  "dense" = list(units = 60, activation = 'relu'),
  "dropout" = list(rate = 0.35),
  "dense" = list(units = 60, activation = 'relu'),
  "dropout" = list(rate = 0.35),
  "dense" = list(units = 40, activation = 'relu'),
  "dropout" = list(rate = 0.35),
  "dense" = list(units = ncol(Y), activation = 'linear')
)

decision_layers <- list(
  "dense" = list(units = 25, activation = 'relu'),
  "dropout" = list(rate = 0.08),
  "dense" = list(units = 45, activation = 'relu'),
  "dropout" = list(rate = 0.08),
  "dense" = list(units = 45, activation = 'relu'),
  "dropout" = list(rate = 0.08),
  "dense" = list(units = 25, activation = 'relu'),
  "dropout" = list(rate = 0.08),
  "dense" = list(units = ncol(Y), activation = 'linear')
)

## Generate the layer tensors
keras::k_clear_session()
main_input <- layer_input(shape = c(ncol(X)), name = 'main_input')

## Connect the inputs
dense_net <- MLP(layers = decision_layers)
predictions <- main_input %>% dense_net

## Make the model
model <- keras_model(inputs = main_input, outputs = predictions)

## Compile the model with the selected loss and optimizer
model %>% compile(
  loss = 'mean_squared_error',
  # optimizer = optimizer_rmsprop(),
  optimizer = optimizer_nadam(lr=0.002),
  metrics = c('mae')
)

## Train the model
history <- model %>% fit(
  x = data_splits$train$X,
  y = data_splits$train$Y, 
  epochs = 250, batch_size = 256, 
  # validation_split = 0.20
  validation_data = list(data_splits$val$X, data_splits$val$Y)
)

keras::save_model_hdf5(model, filepath = "~/CurrentProjects/Matt_MacGMC/PMC_Class/model3_024mae_5layer_250epoch_008dropout_nonxx.hdf5")
```

```{r}
model <- keras::load_model_hdf5("~/CurrentProjects/Matt_MacGMC/PMC_Class/model3_033mae_5layer_250epoch_008dropout_withnxx.hdf5")

## See how it performs on the different partitions of the data
model %>% evaluate(data_splits$train$X, data_splits$train$Y)
model %>% evaluate(data_splits$val$X, data_splits$val$Y)
model %>% evaluate(data_splits$test$X, data_splits$test$Y)

```

```{r}
## My OED
layup_normalizer <- normalizer(layup_class)
layup_orientation_normalizer <- normalizer(as.vector(unlist(lam_layups)))

# eta should include the layup and the fiber vf
design_vars <- cbind(layup_class)
eta_normalizer <- normalizer(design_vars)
eta <- eta_normalizer(design_vars) ## designs to be generated

# Q are the unknown constituent properties we would like to optimally infer
constituent_properties <- cbind(matrix_props, fiber_props, fiber_vf)
constituent_properties_normalizer <- normalizer(constituent_properties)
Q <- constituent_properties_normalizer(constituent_properties)

# Y is the outcome E, UTS, and PLS
ss_predicted_norm <- predict(model, as.matrix(X))
ss_predicted <- Y_normalizer(ss_predicted_norm, invert = TRUE)
Y = ss_predicted_norm


{
idx = 2
num = length(layups)
start = (idx-1)*num+1
ii <- start - 1
sapply(res_data[start:(start+num-1)], FUN = function(data){
  ii <<- ii + 1
  ind = ii %% num
  max_y = max(c_ss_props[ii,1], ss_predicted[ii,1])
  if (ind == 0) {ind = num}
  tit = layups[ind]
  plot(data$V1, data$V2, col=alpha('black', 1), xlab='strain', ylab='stress', main=tit, ylim = range(0:max_y))
  abline(0,res_ss_props[ii,5], col='red', lwd=3)
  points(res_ss_props[ii,4], res_ss_props[ii,3], pch=4, col='red', lwd=3, cex=2)
  points(res_ss_props[ii,2], res_ss_props[ii,1], pch=1, col='red', lwd=3, cex=2)
  abline(0,ss_predicted[ii,5], col='green', lwd=2)
  points(ss_predicted[ii,4], ss_predicted[ii,3], pch=4, col='green', lwd=3, cex=2)
  points(ss_predicted[ii,2], ss_predicted[ii,1], pch=1, col='green', lwd=3, cex=2)
})

}
```

Plot figures
```{r}
# Predicted and Calculated
{
ii = 13
ind = ii %% num
if (ind == 0) {ind = num}
tit = layups[ind]
x <- res_data[[ii]]$V1
y <- res_data[[ii]]$V2
xrange <- range(0, max(x))
yrange <- range(0, max(y))
plot(xrange, yrange, type='n', xlab='Strain [length/length]', ylab='Stress [MPa]', cex.lab=3, cex.axis=1.8)#, main=sprintf('PMC - %s', tit))
abline(0,res_ss_props[ii,5], col='red', lwd=9)
abline(0,ss_predicted[ii,5], col='green', lwd=5)
points(res_ss_props[ii,4], res_ss_props[ii,3], pch=4, col='red', lwd=5, cex=4)
points(res_ss_props[ii,2], res_ss_props[ii,1], pch=1, col='red', lwd=5, cex=4)
points(ss_predicted[ii,4], ss_predicted[ii,3], pch=4, col='green', lwd=4, cex=4)
points(ss_predicted[ii,2], ss_predicted[ii,1], pch=1, col='green', lwd=4, cex=4)
lines(x, y, type='l', lwd=5, lty=5)
legend('topright', inset=0.02, 
       legend=c("Virtual data", "E calculated", "E predicted", "PLS calculated", "PLS predicted", "UTS calculated", "UTS predicted"),
       col=c("black", "red", "green", "red", "green", "red", "green"),
       lty=c(5,1,1,0,0,0,0),
       pch=c(0,0,0,4,4,1,1),
       lwd=c(2,3,5,0,0,0,0),
       pt.cex=c(0,0,0,3,3,3,3),
       pt.lwd=c(0,0,0,4,4,4,4),
       cex=1.2
       )
}

# Just calculated
{
ii = 13
ind = ii %% num
if (ind == 0) {ind = num}
tit = layups[ind]
x <- res_data[[ii]]$V1
y <- res_data[[ii]]$V2
xrange <- range(0, max(x))
yrange <- range(0, max(y))
plot(xrange, yrange, type='n', xlab='Strain [length/length]', ylab='Stress [MPa]', cex.lab=3, cex.axis=1.8)#, main=sprintf('PMC - %s', tit))
abline(0,res_ss_props[ii,5], col='red', lwd=7)
#abline(0,ss_predicted[ii,5], col='green', lwd=3)
points(res_ss_props[ii,4], res_ss_props[ii,3], pch=4, col='red', lwd=4, cex=4)
points(res_ss_props[ii,2], res_ss_props[ii,1], pch=1, col='red', lwd=4, cex=4)
#points(ss_predicted[ii,4], ss_predicted[ii,3], pch=4, col='green', lwd=4, cex=2)
#points(ss_predicted[ii,2], ss_predicted[ii,1], pch=1, col='green', lwd=4, cex=2)
lines(x, y, type='l', lwd=5, lty=5)
legend('topright', inset=0.02, 
       legend=c("Virtual data", "E calculated", "PLS calculated", "UTS calculated"),
       col=c("black", "red", "red", "red"),
       lty=c(5,1,0,0),
       pch=c(0,0,4,1),
       lwd=c(3,5,0,0),
       pt.cex=c(0,0,3,3),
       pt.lwd=c(0,0,4,4),
       cex=1.2
       )
}

# Just curve
{
ii = 13
ind = ii %% num
if (ind == 0) {ind = num}
tit = layups[ind]
x <- res_data[[ii]]$V1
y <- res_data[[ii]]$V2
xrange <- range(0, max(x))
yrange <- range(0, max(y))
par(mar=c(6,6,2,1))
plot(xrange, yrange, type='n', xlab='Strain [length/length]', ylab='Stress [MPa]', cex.lab=3, cex.axis=1.8)#, main=sprintf('PMC - %s', tit))
lines(x, y, type='l', lwd=5, lty=1, col='blue')
}
```


## Perform new OED 
```{r}

truncate_between <- function(x, a = 0, b = 1){
  x[x < a] <- a
  x[x > b] <- b
  return(x)
}

get_runif <- function(n, mean, percent){
  return(runif(n, mean-mean*percent/100, mean+mean*percent/100))
}

get_design <- function(d){
   return(unlist(lapply(d, function(i) {l2d(i)} )))
}  

## Expected utility function (to give to the approximate coordinate exchange algorithm)
  
# k = 6, fiber E and V, matrix E and V, volume fraction, and laminate type
util <- function(d, B, verbose = TRUE, ...){
  n <- length(d) # number of layups to test in experiment
  
  # The design parameters: layup (this is the eta)
  gen_layup = d
  gen_layup_class <- round(layup_normalizer(gen_layup, invert = TRUE))
  gen_layup_repeat <- matrix(gen_layup_class, nrow=B*n, ncol=1) # repeat design B times for prediction vectorization
  gen_layout_hot <- to_categorical(y = gen_layup_repeat-1L, num_classes = length(layups))

  # We need to generate B random variables for the other parameters (these are the Q)
  E_fiber = get_runif(B, 80000, 25)
  UTS_fiber = get_runif(B, 3800, 25)
  nu_fiber = get_runif(B, 0.25, 20)
  E_matrix = get_runif(B, 4000, 25)
  UTS_matrix = get_runif(B, 80, 40)
  nu_matrix = get_runif(B, 0.35, 10)
  VF = runif(B, 0.4, 0.7)
  
  X_tmp = cbind(E_fiber, nu_fiber, UTS_fiber, E_matrix, nu_matrix, UTS_matrix, VF)
  X_tmp_norm = X_normalizer(X_tmp) 
  
  # Now we need to repeat X_temp_norm for each d so we can vectorize NN predictions outside the loop
  X_tmp_repeat = X_tmp_norm[rep(1:nrow(X_tmp_norm), each=n), 1:ncol(X_tmp_norm)]
  
  # Get predictions (Y)
  X_test = cbind(gen_layout_hot, X_tmp_repeat)
  Q_test <- predict(model, as.matrix(X_test))
  
  # since the design is discreet, we set their distance maximum from eachother
  #z = matrix(seq(-1,1,length.out=n),nrow=n, ncol=1)
  
  #z = gen_layout_hot[(n*i-n+1):(i*n),]
  #X_tmp_repeat <- X_tmp_repeat[,-1] # Drop VF so it doesn't influence CMI
  cmi_res = lapply(1:B, function(i){
    return (MaterialAnalysis::cMI(X=Q_test[(n*i-n+1):(i*n),],
                                  Y = X_tmp_repeat[(n*i-n+1):(i*n),], 
                                  Z = gen_layout_hot[(n*i-n+1):(i*n),], type='ps', k=1L))
  })
  cmi_res = rapply(cmi_res, f=function(x) ifelse(is.nan(x),0,x), how="replace" )

  return(unlist(cmi_res))
}
```

n = 2 calculate all
```{r}


ordering <- c("[0]_24",
            "[15, -15]_6S",
            "[30, -30]_6S",
            "[45, -45]_6S",
            "[60, -60]_6S",
            "[75, -75]_6S",
            "[90]_24",
            "[0/90]_6S", 
            "[0, -60, 60]_4S",
            "[0, -45, 45, 90]_3S", 
            "[0, 45, 90, -45]_3S", 
            "[45, -45, 90, 0]_3S",
            "[0, 90, -30, 30, -60, 60]_2S")

l2d <- function(x){
  2*x/length(layups)-1-1/length(layups)
}

{
lay1 <- c()
lay2 <- c()
val <- c()
count <- 1L
for (i in 1:length(layups)){
  print(layups[round(layup_normalizer(l2d(i), invert = TRUE))])
  for (j in 1:i){
    v = mean(util(c(l2d(i), l2d(j)),1000, k=1, alpha=0.7))
    lay1[[count]] <- layups[i]
    lay2[[count]] <- layups[j]
    val[[count]] <- v
    count = count + 1
    lay1[[count]] <- layups[j]
    lay2[[count]] <- layups[i]
    val[[count]] <- v
    count = count + 1
  }}
m = data.frame(rowname = lay1, colname=lay2, value=val)
}

zeros = m %>% filter(value == 0)

m$rowname <- factor(m$rowname, levels = ordering)
m$colname <- factor(m$colname, levels = ordering)
{
#m$value[m$value == 0] <- min(m$value[m$value>0]) * 0.9
ggplot(m, aes(x = rowname, y = colname, fill = value)) +
  geom_tile() +
  coord_equal() +
    scale_fill_viridis_c(limits=c(min(m[m$value>0,3]),max(m$value))) +
    theme(axis.text = element_text(size=12)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    theme(axis.title=element_text(size=15, face="bold")) +
    labs(fill = "CMI", x = "Layup 1", y = "Layup 2") +
    geom_tile(data = zeros, aes(x = rowname, y = colname), fill = "black")
  
ggsave("~/CurrentProjects/Matt_MacGMC/PMC_Class/d=2_nxy=1_VF=0.jpg")
}
m[order(m$value, decreasing=TRUE),]


{
lay1 <<- c()
lay2 <<- c()
val <<- c()
count <- 1
combn(length(layups),2, function(i){
    v = mean(util(c(l2d(i[1]), l2d(i[2])),1000, k=1, alpha=0.7))
    lay1[[count]] <<- layups[i[1]]
    lay2[[count]] <<- layups[i[2]]
    val[[count]] <<- v
    count <<- count + 1
  })
m2 = data.frame(first = lay1, second=lay2, value=val)
}
```

n = 3 calculate all
```{r}

l2d <- function(x){
  2*x/length(layups)-1-1/length(layups)
}

{
lay1 <- c()
lay2 <- c()
lay3 <- c()
val <- c()
count <- 1L
for (i in 1:length(layups)){
  print(layups[round(layup_normalizer(l2d(i), invert = TRUE))])
  for (j in 1:i){
    for (k in 1:j){
      v = mean(util(c(l2d(i), l2d(j), l2d(k)),1000, k=1, alpha=0.7))
      
      lay1[[count]] <- layups[i]
      lay2[[count]] <- layups[j]
      lay3[[count]] <- layups[k]
      val[[count]] <- v
      count = count + 1
      
      lay1[[count]] <- layups[i]
      lay2[[count]] <- layups[k]
      lay3[[count]] <- layups[j]
      val[[count]] <- v
      count = count + 1
      
      lay1[[count]] <- layups[j]
      lay2[[count]] <- layups[i]
      lay3[[count]] <- layups[k]
      val[[count]] <- v
      count = count + 1
      
      lay1[[count]] <- layups[j]
      lay2[[count]] <- layups[k]
      lay3[[count]] <- layups[i]
      val[[count]] <- v
      count = count + 1
      
      lay1[[count]] <- layups[k]
      lay2[[count]] <- layups[i]
      lay3[[count]] <- layups[j]
      val[[count]] <- v
      count = count + 1
      
      lay1[[count]] <- layups[k]
      lay2[[count]] <- layups[j]
      lay3[[count]] <- layups[i]
      val[[count]] <- v
      count = count + 1
  }}}
m = data.frame(rowname = lay1, colname=lay2, third=lay3, value=val)
}

# Old pdf
{
m$value[m$value == 0] <- min(m$value[m$value>0]) * 0.9
pdf("~/CurrentProjects/Matt_MacGMC/PMC_Class/d=3_nxy=0_new.pdf")
lapply(layups, function(x) {
  this_m <- subset(m, third == x)
  print(ggplot(this_m, aes(x = rowname, y = colname, fill = value)) +
  geom_tile() +
    ggtitle(x) +
    scale_fill_viridis_c(limits=c(min(m$value),max(m$value))) +
    labs(colour = "CMI", x = "Layup 1", y = "Layup 2") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)))
    
})
dev.off()
}

subm = m[!duplicated(m$value),]
subm[order(subm$value, decreasing=TRUE),]

# For paper
zeros = m %>% filter(value == 0)
m$rowname <- factor(m$rowname, levels = ordering)
m$colname <- factor(m$colname, levels = ordering)
m$third <- factor(m$third, levels = ordering)

scaleFUN <- function(x) sprintf("%.2f", x)

lapply(layups, function(x) {
  this_m <- subset(m, third == x)
  zeros = this_m %>% filter(value == 0)
  ggplot(this_m, aes(x = rowname, y = colname, fill = value)) +
  geom_tile() +
  coord_equal() +
    scale_fill_viridis_c(limits=c(min(m[m$value>0,4]),max(m$value)), labels = scaleFUN) +
    theme(axis.text = element_text(size=12)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(fill = "CMI", x = "Layup 1", y = "Layup 2") +
    theme(axis.title=element_text(size=15, face="bold")) +
    geom_tile(data = zeros, aes(x = rowname, y = colname), fill = "black")
  x = str_replace(x, '/', '_')
  path = sprintf("~/CurrentProjects/Matt_MacGMC/PMC_Class/d=3_nxy=0_VF=0_%s.jpg", x)
  print(path)
  ggsave(path)
})


{
lay1 <<- c()
lay2 <<- c()
lay3 <<- c()
val <<- c()
count <- 1
combn(length(layups),3, function(i){
    v = mean(util(c(l2d(i[1]), l2d(i[2]), l2d(i[3])),1000, k=1, alpha=0.7))
    lay1[[count]] <<- layups[i[1]]
    lay2[[count]] <<- layups[i[2]]
    lay3[[count]] <<- layups[i[3]]
    val[[count]] <<- v
    count <<- count + 1
  })
m3 = data.frame(first = lay1, second=lay2, third=lay3, value=val)
}

```

n = 4 calculate all
```{r}
{
lay1 <<- c()
lay2 <<- c()
lay3 <<- c()
lay4 <<- c()
val <<- c()
count <- 1
combn(length(layups),4, function(i){
    v = mean(util(c(l2d(i[1]), l2d(i[2]), l2d(i[3]), l2d(i[4])),100, k=1, alpha=0.7))
    lay1[[count]] <<- layups[i[1]]
    lay2[[count]] <<- layups[i[2]]
    lay3[[count]] <<- layups[i[3]]
    lay4[[count]] <<- layups[i[4]]
    val[[count]] <<- v
    count <<- count + 1
  })
m4 = data.frame(first = lay1, second=lay2, third=lay3, fourth=lay4, value=val)
}

```

n = 5 calculate all
```{r}

{
lay1 <<- c()
lay2 <<- c()
lay3 <<- c()
lay4 <<- c()
lay5 <<- c()
val <<- c()
count <- 1
combn(length(layups),5, function(i){
    v = mean(util(c(l2d(i[1]), l2d(i[2]), l2d(i[3]), l2d(i[4]), l2d(i[5])),100, k=1, alpha=0.7))
    lay1[[count]] <<- layups[i[1]]
    lay2[[count]] <<- layups[i[2]]
    lay3[[count]] <<- layups[i[3]]
    lay4[[count]] <<- layups[i[4]]
    lay5[[count]] <<- layups[i[5]]
    val[[count]] <<- v
    count <<- count + 1
  })
m5 = data.frame(first = lay1, second=lay2, third=lay3, fourth=lay4, fifth = lay5, value=val)
}

```

Ace
```{r}

{n <- 3; k <- 1}
res <- vector(mode = "list", length = 5L)
#devtools::document()
for (i in 1:length(res)){
  print(i)
  start.d <- matrix(2 * randomLHS(n = n, k = k) - 1, nrow = n, ncol = k)
  #util <- makeUTILITY()
  res[[i]] <- acebayes::ace(utility = util, start.d = start.d, B=c(1000,1000),
                            deterministic = FALSE, 
                            lower = matrix(-1, nrow = n, ncol = k), upper = matrix(1, nrow = n, ncol = k), 
                            N1 = 10, N2=10, Q = 100, progress=TRUE
                            )
  save(res, file = "~/CurrentProjects/Matt_MacGMC/PMC_Class/ACE_n5.rdata")
}

load("~/MAC/OED/res7_n2_c1000-100_n1-20_n-20_Q20_L30.rdata")
```

Plot results of OED
```{r}

optimal_design = sapply(1:length(res), function(i){
  return (layup_normalizer(res[[i]]$phase2.d, invert = TRUE))
})

optimal_design_names = sapply(optimal_design, function(x){
  return (layups[round(x)])
})
optimal_design_names = t(matrix(optimal_design_names, nrow = n, ncol = length(res)))

par(mar = c(12,5,5,5))
barplot(table(optimal_design_names) ,main="Layup sensativities",ylab="Freqency",xlab="",las=2)
```